TurtleBot SLAM

### 2013-01-23 trunk/Article/Article.tex

\begin{abstract}
 This article describes an implementation of Graph-based Simultaneous Localization And Mapping (Graph SLAM) with frontier-based exploration. The challenge of the SLAM-problem is building a map of the robot's environment and localizing it using uncertain measurement data. Robot localization needs knowledge of the map and vice-versa. Another challenge is finding a strategy to efficiently explore the robot's environment. A Graph SLAM algorithm and a Wavefront frontier detection algorithm have been implemented to solve these problems. This article gives an insight into the implementation process of these algorithms. The implementation is tested and validated in a simulator. The result of the process is a fully explored sample environment.
\end{abstract}

>>>>

\begin{abstract}
 This article describes an implementation of Graph-based Simultaneous Localization And Mapping (Graph SLAM) with frontier-based exploration. The challenge of the SLAM-problem is building a map of the robot's environment and localizing it using uncertain measurement data. Robot localization needs knowledge of the map and vice-versa. Another challenge is finding a strategy to efficiently explore the robot's environment. A Graph SLAM algorithm and a Wavefront frontier detection algorithm have been implemented to solve these problems. This article gives an insight into the field of robotics and into the implementation process of the suggested algorithms. The resulting program is tested and validated in a simulator. The final product is able to fully explore an environment autonomously and to create a map during the exploration process.
\end{abstract}
